maxent model avec xvalidation (year-based test training)

### 2019-05-13 src/maxent_avec_xvalidation.Rmd
ops

select month
```{r month of interest -change}
mthna <- "dec"
mthno <- "12"
```

@@

binstack <- stack(binaryprob_list)
stacksum <- sum(binstack, na.rm = TRUE)
writeRaster(stastaccksum, paste0("../output/maxent/predictions/", mthna, "/binary_highavg_2d.asc"), overwrite=TRUE)
plot(stacksum, png(paste0("../output/maxent/predictions/", mthna, "/binary_highprob_avg_2d.png")))
dev.off()
```
```{r med probability average map per year 2D representation}
binaryprob_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^binary_avg_medprob.*.asc", full.names = TRUE)

>>>>

select month
```{r month of interest -change}
mthna <- "jan"
mthno <- "1"
```

@@

binstack <- stack(binaryprob_list)
stacksum <- sum(binstack, na.rm = TRUE)
writeRaster(stacksum, paste0("../output/maxent/predictions/", mthna, "/binary_highavg_2d.asc"), overwrite=TRUE)
plot(stacksum, png(paste0("../output/maxent/predictions/", mthna, "/binary_highprob_avg_2d.png")))
dev.off()
```
```{r med probability average map per year 2D representation}
binaryprob_list <- list.files(paste0("../output/maxent/predictions/", mthna), pattern = "^binary_avg_medprob.*.asc", full.names = TRUE)
